Análisis Inteligente de Datos y Visualización aplicadas a la Investigación Criminal\thanks{Universidad Nacional del Sur - Bahía Blanca - Argentina. Universidad Nacional de la Patagonia San Juan Bosco - Chubut - Argentina.}

### 2022-05-02 marco-trabajo.tex
Se acomodan algunas cosas qque surgieron en la última reunión

Su progreso, mantenimiento y mejora continua está a cargo de un Equipo de Desarrollo del Departamento de Informática del Área de Planificación y Control de Gestión de la Procuración General, del cual formo parte.
\todo{Hablo en singular? plural?}

@@

\begin{figure}
	\centering
	\tikzstyle{nodoA}= [circle,fill=blue!25,minimum size=40pt]
	\tikzstyle{nodoB}=[circle,fill=blue!25,minimum size=20pt]
	\begin{center}
		\begin{tikzpicture}[scale=1.0]
			\node[nodoA][draw] (1) at (0,5) {A};
			\node[nodoB][draw] (2) at (4,5) {B};
			%
			\draw [line width=0.8mm, red ] (1) -- (2);
		\end{tikzpicture}
	\end{center}
	\caption{Ejemplo de relación entre dos personas.} 
	\label{fig:grafode2}
\end{figure}

>>>>

Su progreso, mantenimiento y mejora continua está a cargo de un Equipo de Desarrollo del Departamento de Informática del Área de Planificación y Control de Gestión de la Procuración General.

@@

\begin{figure}
	\centering
	\tikzstyle{nodoA}= [circle,fill=blue!25,minimum size=60pt]
	\tikzstyle{nodoB}=[circle,fill=blue!25,minimum size=30pt]
	\tikzstyle{nodoC}=[circle,fill=blue!25,minimum size=20pt]
	\begin{center}
		\begin{tikzpicture}[scale=1.0]
			\node[nodoA][draw] (1) at (0,6) {A};
			\node[nodoB][draw] (2) at (4,5) {B};
			\node[nodoC][draw] (3) at (4,7) {C};
			%
			\draw [line width=2.8mm, red ] (1) -- (2);
			\draw [line width=0.8mm, red ] (1) -- (3);
		\end{tikzpicture}
	\end{center}
	\caption{Ejemplo de relación entre tres personas.} 
	\label{fig:grafode2}
\end{figure}

### 2022-05-02 paper-swahler-jaiio2022.tex
Se acomodan algunas cosas qque surgieron en la última reunión

\section{Análisis de Redes Sociales (SNA)}
\todo{Ver si no es una sub-sección de la introducción}
\input{sna}

\section{Marco de Trabajo - Ministerio Público Fiscal del Chubut}
\todo{Quizás deba estar incluído en otra sección ó subsección}
\input{marco-trabajo}

@@

\section{Resultados}
\input{resultados}

@@

\section{Conclusión}
\input{conclusion}

\todo{Dejo los ejemplos del template como ayuda}
\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

\subsubsection{Acknowledgements} Please place your acknowledgments at
the end of the paper, preceded by an unnumbered run-in heading (i.e.
3rd-level heading).

>>>>

\section{Análisis de Redes Sociales (SNA)}
\input{sna}

\section{Marco de Trabajo - Ministerio Público Fiscal del Chubut}
\input{marco-trabajo}

@@

@@

\section{Conclusiones}
\input{conclusion}

%\todo{Dejo los ejemplos del template como ayuda}
%\paragraph{Sample Heading (Fourth Level)}
%The contribution should contain no more than four levels of
%headings. Table~\ref{tab1} gives a summary of all heading levels.
%
%\begin{table}
%\caption{Table captions should be placed above the
%tables.}\label{tab1}
%\begin{tabular}{|l|l|l|}
%\hline
%Heading level &  Example & Font size and style\\
%\hline
%Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
%1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
%2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
%3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
%4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
%\hline
%\end{tabular}
%\end{table}
%
%
%\noindent Displayed equations are centered and set on a separate
%line.
%\begin{equation}
%x + y = z
%\end{equation}
%Please try to avoid rasterized images for line-art diagrams and
%schemas. Whenever possible, use vector graphics instead (see
%Fig.~\ref{fig1}).
%
%\begin{figure}
%\includegraphics[width=\textwidth]{fig1.eps}
%\caption{A figure caption is always placed below the illustration.
%Please note that short captions are centered, while long ones are
%justified by the macro package automatically.} \label{fig1}
%\end{figure}
%
%\begin{theorem}
%This is a sample theorem. The run-in heading is set in bold, while
%the following text appears in italics. Definitions, lemmas,
%propositions, and corollaries are styled the same way.
%\end{theorem}
%%
%% the environments 'definition', 'lemma', 'proposition', 'corollary',
%% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%%
%\begin{proof}
%Proofs, examples, and remarks have the initial word in italics,
%while the following text appears in normal font.
%\end{proof}
%For citations of references, we prefer the use of square brackets
%and consecutive numbers. Citations using labels or the author/year
%convention are also acceptable. The following bibliography provides
%a sample reference list with entries for journal
%
%%articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
%%book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
%%and a homepage~\cite{ref_url1}. Multiple citations are grouped
%%\cite{ref_article1,ref_lncs1,ref_book1},
%%\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
%\subsubsection{Acknowledgements} Please place your acknowledgments at
%the end of the paper, preceded by an unnumbered run-in heading (i.e.
%3rd-level heading).

### 2022-05-02 titulo.tex
Se acomodan algunas cosas qque surgieron en la última reunión

\title{Análisis Inteligente de Datos y Visualización aplicadas a la Investigación Criminal\\
Intelligent Data Analysis and Visualization applied to Criminal Investigation
\thanks{Universidad Nacional del Sur - Bahía Blanca - Argentina. Universidad Nacional de la Patagonia San Juan Bosco - Chubut - Argentina.}}
%
\titlerunning{Análisis y Visualización de Redes de Datos aplicada a la Justicia

Analysis and Visualization of Data Networks applied to Justice}
%

% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Sebastián P. WAHLER\inst{1} \and
	Diego C. MARTÍNEZ\inst{1} \and
	Martín L. LARREA\inst{1}}
%
\authorrunning{S. Wahler, D. Martínez, M. Larrea}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Departamento de Ciencias e Ingeniería de la Computación, Universidad Nacional del Sur, Av. Alem 1253, B8000CPB Bahía Blanca, ARGENTINA.
	\email{spwahler@ing.unp.edu.ar, dcm@cs.uns.edu.ar, mll@cs.uns.edu.ar}\\
	\url{https://cs.uns.edu.ar/}}
%

>>>>

\title{Análisis Inteligente de Datos y Visualización aplicadas a la Investigación Criminal\\
Intelligent Data Analysis and Visualization applied to Criminal Investigation
\thanks{Universidad Nacional de la Patagonia San Juan Bosco - Chubut - Argentina.\\Universidad Nacional del Sur - Bahía Blanca - Argentina.}}
%
\titlerunning{Análisis y Visualización de Redes de Datos aplicada a la Justicia}
%
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Sebastián P. WAHLER\inst{1} \inst{2} \and Diego C. MARTÍNEZ\inst{3} \and Martín L. LARREA\inst{3}}
%
\authorrunning{S. Wahler, D. Martínez, M. Larrea}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
	\inst{}Departamento de Informática, Facultad de Ingeniería, Universidad Nacional de la Patagonia San Juan Bosco, Mitre 655, U9100, Trelew, ARGENTINA.\\
	\email{spwahler@ing.unp.edu.ar}\\
	\url{http://www.ing.unp.edu.ar/dpto-informatica.html}
	\and
	\inst{}Departamento de Informática, Procuración General, Ministerio Público Fiscal, Poder Judicial de la Provincia del Chubut, Belgrano 521, U9102, Rawson, ARGENTINA.\\
	\email{swahler@juschubut.gov.ar}\\
	\url{https://www.mpfchubut.gov.ar}
	\and
	\inst{}Departamento de Ciencias e Ingeniería de la Computación, Universidad Nacional del Sur, Av. Alem 1253, B8000CPB Bahía Blanca, ARGENTINA.\\
	\email{dcm@cs.uns.edu.ar, mll@cs.uns.edu.ar}\\
	\url{https://cs.uns.edu.ar/}
}
%
